### 2017-11-02 manuscript.rmd
added mclapply

```{r estimate_tau_model, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
	# Estimate model parameters and add them to the tree objects
	# Subcalls to fitContinuous() are parallel, so don't use mclapply here
	# This takes a while, so do it once here and reuse the values as needed
	gene_trees_calibrated = lapply( gene_trees_calibrated, add_model_parameters )
```

>>>>

```{r estimate_tau_model, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
	# Estimate model parameters and add them to the tree objects
	# This takes a while, so do it once here and reuse the values as needed
	gene_trees_calibrated = mclapply( 
		gene_trees_calibrated, 
		add_model_parameters, 
		mc.cores=cores 
	)
```
